MCC Kids Model Predictions

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
move files

@@

pref_post_con_same<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

@@

>>>>

      var priorProbs= [1-priorReg,1-priorReg, priorReg]

@@

pref_post_con_same2<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

@@

# 2 vs object world

```{r posterior preference congruent}
postPrefConWebppl2 <- '

pref_post_con_same2<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl2 , sep='\n'),
  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

prefPostPredConSame2 <- pref_post_con_same2%>%
  spread(Parameter, value)

pref_post_con_same2 <- pref_post_con_same2%>%
  mutate(chain = factor(Chain))%>%
  mutate(alignment = "congruent",
         condition = "same speaker")

post_predictions_con_same2 <- sapply(1:length(prefPostPredConSame2$pref_int), function(idx) {
            plogis(prefPostPredConSame2$pref_int[idx] + prefPostPredConSame2$pref_slope[idx] * x_plot)
        })

colnames(post_predictions_con_same2) <- 1:length(prefPostPredConSame2$pref_int)
plot_post_data_con_same2 <- as.data.frame(cbind(x_plot, post_predictions_con_same2))
plot_post_data_con_same2 <- melt(plot_post_data_con_same2, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")%>%
  mutate(alignment = "congruent",
         condition = "same speaker",
         world = "2 objects")

x <- bind_rows(
  plot_post_data_con_same2,
  plot_post_data_con_same
)

x_mean <- x%>%
  group_by(world,x_plot)%>%
  summarise(mean = mean(y_plot),
            ci_upper = hdi_upper(y_plot),
            ci_lower = hdi_lower(y_plot))

a <- prefPostPredConSame2%>%
  summarise(mean_int = mean(pref_int),
            mean_slope = mean(pref_slope))%>%
  expand(y = plogis(mean_int + mean_slope * x_plot))%>%
  mutate(x = x_plot,
         world = "2 objects")

b <- prefPostPredConSame%>%
  summarise(mean_int = mean(pref_int),
            mean_slope = mean(pref_slope))%>%
  expand(y = plogis(mean_int + mean_slope * x_plot))%>%
  mutate(x = x_plot,
         world = "3 objects")

c <- bind_rows(a,b)

ggplot(x) + 
  geom_line(aes(x_plot, y_plot, group = iteration), col = "grey", alpha = 0.2) + 
  geom_ribbon(data = x_mean, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "darkgreen", alpha = 0.3) +
  geom_line(data = x_mean, aes(x_plot, mean), col = "black") + 
  geom_line(data = c, aes(x, y), col = "red") + 
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
  scale_y_continuous(limits = c(0, 1), name="P in favor of preferred object")+
  facet_grid(~world)+
  theme_few()
